Consistent Polyhedral Surrogates via Embeddings

### 2019-05-17 neurips-19/poly-embed.tex
minor comment
Labeling theorem that was missing

\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.

>>>>

\begin{theorem}\label{thm:polyhedral-embed}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\jessie{Cut the definition of refines, so maybe we just want the first part of this.}
\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.
